# Data Quality Check

## Import libraries

```{r}
library(bupaverse)
library(daqapo)
```

## Read XES

```{r}
# event_log <- xesreadR::read_xes("../2_to_xes/mimicel.xes", validate = FALSE)
```

When import XES file into `bupaR`, it will prompt the following error messages. Hence, we use CSV file to assess the data quality of event log instead.

```         
Error: cannot allocate vector of size 1.6 Gb
10. id(list(col_id, row_id), drop = FALSE)
9. spread.data.frame(., type, value)
8. spread(., type, value)
7. select(., -attr_id)
6. list2(...)
5. bind_cols(., eventlog)
4. select(., -n_attributes, -attr_id)
3. spread(., key, value)
2. all_attrs %>% unlist() %>% as_data_frame() %>% mutate(type = rep(c("key",
"value"), length = nrow(.)), attr_id = rep(1:(nrow(.)/2),
each = 2)) %>% spread(type, value) %>% select(-attr_id) %>%
bind_cols(eventlog) %>% select(-n_attributes, -attr_id) %>% ...
1. xesreadR::read_xes("../2_to_xes/mimicel.xes", validate = FALSE)
```

## Read CSV

Import event log form csv

```{r}
eventlog_df <- 
  read.csv('../2_to_xes/mimicel.csv', sep=",", na.strings = c("", " "))
```

Convert dataframe to event log and activity log , add activity_instance_id, add lifecycle_id

```{r}
eventlog_df %>%
  bupaR::convert_timestamps(columns="timestamps", format = ymd_hms) %>%
  bupaR::mutate(resource_id = NA) %>%
  bupaR::mutate(lifecycle_id = "complete") %>%
  bupaR::mutate(activity_instance_id = as.numeric(row.names(.))) %>%
  bupaR::eventlog(case_id = "stay_id",
                  activity_id = "activity",
                  activity_instance_id = "activity_instance_id",
                  timestamp = "timestamps",
                  lifecycle_id = "lifecycle_id",
                  resource_id = "resource_id") -> event_log

# package `daqapo` requires `activitylog` for validating data quality
event_log %>% 
  bupaR::to_activitylog() -> activity_log
```

## Inspect `event_log`

Show identifiers for `event_log`

```{r}
event_log %>% bupaR::mapping()
```


Show activity, event, case, and trace of `event_log`

```{r}
event_log %>% bupaR::n_activities()
event_log %>% bupaR::n_events()
event_log %>% bupaR::n_cases()
event_log %>% bupaR::n_traces()

```
Show unique activities

```{r}
event_log %>% 
  bupaR::activities()
```

Show unique traces

```{r}
event_log %>% bupaR::traces()
```

## Data Quality Assessment

The table below summarizes the different data quality assessment tests available in `daqapo`, after which each test will be briefly demonstrated.

| Function name                        | Description                                                                                                                               | Output                                                                             |
|:-----------------|:--------------------------------|:--------------------|
| detect_activity_frequency_violations | Function that detects activity frequency anomalies per case                                                                               | Summary in console + Returns activities in cases which are executed too many times |
| detect_attribute_dependencies        | Function detecting violations of dependencies between attributes (i.e. condition(s) that should hold when (an)other condition(s) hold(s)) | Summary in console + Returns rows with dependency violations                       |
| detect_missing_values                | Function detecting missing values at different levels of aggregation                                                                      | Summary in console + Returns rows with NAs                                         |
| detect_multiregistration             | Function detecting the registration of a series of events in a short time period for the same case or by the same resource                | Summary in console + Returns rows with multiregistration on resource or case level |
| detect_unique_values                 | Function listing all distinct combinations of the given log attributes                                                                    | Summary in console + Returns all unique combinations of values in given columns    |
| detect_value_range_violations        | Function detecting violations of the range of acceptable values                                                                           | Summary in console + Returns rows with value range infringements                   |

### Detect activity frequency anomalies

```{r}
activity_log %>% daqapo::detect_activity_frequency_violations("Enter the ED" = 1, "Triage in the ED" = 1)
```


### 1. Detect Missing Values

Overview missing values for each column

```{r}
activity_log %>%
  daqapo::detect_missing_values(level_of_aggregation = "overview")
  
```

Detect missing values for `subject_id`

```{r}
activity_log %>% 
  daqapo::detect_missing_values(level_of_aggregation = "column", 
                                column = "subject_id")

```

Detect missing values for `gender`

```{r}
activity_log %>% 
  bupaR::filter(activity=="Enter the ED") %>%
  daqapo::detect_missing_values(level_of_aggregation = "column", 
                                column = "gender")

```

Detect missing values for `race`

```{r}
activity_log %>% 
  bupaR::filter(activity=="Enter the ED") %>%
  daqapo::detect_missing_values(level_of_aggregation = "column", 
                                column = "race")
```

Detect missing values for `arrival_transport`

```{r}
activity_log %>% 
  bupaR::filter(activity=="Enter the ED") %>%
  daqapo::detect_missing_values(level_of_aggregation = "column", 
                                column = "arrival_transport")
```

Detect missing values for `disposition`

```{r}
activity_log %>% 
  bupaR::filter(activity=="Discharge from the ED") %>%
  daqapo::detect_missing_values(level_of_aggregation = "column", 
                                column = "disposition")
```

Detect missing values for `acuity`

```{r}
activity_log %>% 
  bupaR::filter(activity=="Triage in the ED") %>%
  daqapo::detect_missing_values(level_of_aggregation = "column", 
                                column = "acuity")
```

### 2. Detect Incomplete Cases

```{r}
activity_log %>%
  daqapo::detect_incomplete_cases(activities = c("Enter the ED", "Triage in the ED", "Discharge from the ED"))
```

### 3. Detect Activity Order Violation

```{r}
activity_log %>% 
  bupaR::filter((activity == "Enter the ED") | ((activity == "Discharge from the ED") & (is.na(seq_num) | seq_num == 1))) -> simple_mimicel

  
```

```{r}
simple_mimicel %>% 
  daqapo::detect_activity_order_violations(activity_order = c("Enter the ED", "Discharge from the ED"), timestamp = "complete")

```

### 4. Detect Attributes Dependencies

Detect cases with `disposition == "ADMITTED"` which `hadm_id` is NA

```{r}
activity_log %>% 
  bupaR::filter((activity =="Discharge from the ED") & (is.na(seq_num) | seq_num == 1) ) %>%
  daqapo::detect_attribute_dependencies(antecedent = (disposition == "ADMITTED"),
                                        consequent = is.na(hadm_id))

```

### 5. Detect_time_anomalies

```{r}
activity_log %>% 
  bupaR::filter((activity == "Enter the ED")) %>%
  bupaR::mutate(enter_time = complete) -> activity_enter

activity_log %>% 
  bupaR::filter(((activity == "Discharge from the ED") & (is.na(seq_num) | seq_num == 1))) %>%
  bupaR::mutate(discharge_time = complete) -> activity_discharge

base::merge(x = activity_enter, y = activity_discharge, all.x = TRUE, by = "stay_id") %>%
  bupaR::mutate(complete = discharge_time) %>%
  bupaR::mutate(start = enter_time) %>%
  daqapo::detect_time_anomalies()
  
```

### 6. Detect Multiregistration

Detect Multiregistration for activity `Medicine reconciliation`

```{r}
activity_log %>%
  bupaR::filter(activity == "Medicine reconciliation") %>%
  daqapo::detect_multiregistration(level_of_aggregation = "case",
                                   timestamp = "complete",
                                   threshold_in_seconds = 61)
```

Detect Multiregistration for activity `Medicine dispensations`

```{r}
activity_log %>%
  bupaR::filter(activity == "Medicine dispensations") %>%
  daqapo::detect_multiregistration(level_of_aggregation = "case",
                                   timestamp = "complete",
                                   threshold_in_seconds = 61)
```

Detect Multiregistration for activity `Vital sign check`

```{r}
activity_log %>%
  filter(activity == "Vital sign check") %>%
  daqapo::detect_multiregistration(level_of_aggregation = "case",
                                   timestamp = "complete",
                                   threshold_in_seconds = 61)
```

Detect Multiregistration for activity `Discharge from the ED`

```{r}
activity_log %>%
  filter(activity == "Discharge from the ED") %>%
  daqapo::detect_multiregistration(level_of_aggregation = "case",
                                   timestamp = "complete",
                                   threshold_in_seconds = 1)
```

### 7. Detect Value Range Violations

Detect invalid value range of *acuity*

```{r}
activity_log %>%
  bupaR::filter(activity == "Triage in the ED") %>%
  daqapo::detect_value_range_violations(acuity = domain_numeric(from=1, to=5))
```

Detect invalid value range of *pain*

```{r}
activity_log %>%
  bupaR::filter(activity == "Triage in the ED" | activity == "Vital sign check") %>%
  bupaR::mutate(pain_num = as.numeric(pain)) %>%
  daqapo::detect_value_range_violations(pain_num = domain_numeric(from=0, to=10))


```
